Qualities of Volunteering and Life Satisfaction: A multiple linear regression model

### 2022-04-27 outputs/paper/paper.Rmd
datasheet complete

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of social trends in order to monitor changes in the living conditions and well-being of Canadians and to provide information on specific social policy issues on the topic of Giving, Volunteering and Participating.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Statistics Canada
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Statistics Canada
4. *Any other comments?*
    - No.

@@

	- It is a sample of the Canadian population. It was obtained by rejective sampling to focus on the subgroup of the population that are volunteers, so it is not representative of the distribution of volunteers in the population.

@@

	- TBD

@@

	- TBD

@@

	- Certain questions in the survey were skipped

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Not to my knowledge.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No.
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is available through CHASS.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- It is already available.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

>>>>

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of social trends in order to monitor changes in the living conditions and well-being of Canadians and to provide information on specific social policy issues on the topic of Giving, Volunteering and Participating.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Statistics Canada
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Government of Canada
4. *Any other comments?*
    - No.

@@

	- The survey was completed by a sample of the Canadian population. The sample was obtained by rejective sampling to focus on the subgroup of the population that are volunteers, so it is not representative of the distribution of volunteers in the population.

@@

	- Each instance consists of the text answers to the questions in the survey on the topics of volunteering (such as quality of volunteer experience, reasons for volunteering, history of volunteering), giving (number of donations, amounts for each donation, reasons for giving), participating (youth experiences) and other socio-demographic characteristics (such as age, martial status, education, occupation, birthplace).

@@

	- No.

@@

	- No.

@@

	- N/A

@@

	- The dataset is self-contained.

@@

	- The data is a public use microdata file (PUMF) so it has been anonymized.

@@

	- Yes, there are flags for if the respondent is a formal volunteer, informal volunteer and giver.

@@

	- No, the data is a public use microdata file (PUMF) so it has been anonymized.

@@

	- No. Although religious affiliation is a flag (has a religious affiliation or not), the specific denomination is not included.

@@

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was reported by subjects. At every stage of processing of the data, Statistics Canada made efforts to verify the data such as by identifying and eliminating potential duplicate records and dropping non-response and out-of-scope records.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Data were collected electronically as a self-completed questionnaire (rEQ) and via computer assisted telephone interviews (iEQ).
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- Participants were first chosen using simple random sampling within geographical strata, and then rejective sampling was used on these samples to obtain more candidates within the population of interest, which is volunteers. 
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- There were interviewers in the data collection process, but their compensation was not specified. 
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- September 4th to December 28th, 2018
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was obtained using SDA @ CHASS at the University of Toronto.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- N/A
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- N/A
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- N/A
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A
12. *Any other comments?*
	- No.

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Statistics Canada: Verification was performed to identify and eliminate potential duplicate records and to drop non-response and out-of-scope records. Records with missing or incorrect information were, in a small number of cases, corrected deterministically or imputed from other information on the questionnaire.
	- Using the provided data, I transformed some variables into binary responses, for example the 'Quality of Volunteer Experience' variables which were originally rated on a 5-degree scale from Strongly disagree to Strongly Agree.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data has not been made available.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- I used R [@citeR] for all data processing.
4. *Any other comments?*
	- No.

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- In this paper, the dataset is used to build multiple linear regression models to investigate the relationship between volunteering and life satisfaction.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The repository to reproduce this paper can be found at https://github.com/KCtt457/gssvolunteering2018.
3. *What (other) tasks could the dataset be used for?*
	- Analysis of trends in the patterns of Giving, Volunteering and Participating in Canada.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Since the data was collected by rejective sampling, one cannot use it to make claims about the distribution of proportion of volunteers in the wider population of Canada. Otherwise, I did not identify any risks or harms of the dataset.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No.
6. *Any other comments?*
	- No.

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is available to subscribing institutions as listed on the [Statistics Canada website](https://www150.statcan.gc.ca/n1/pub/11-625-x/11-625-x2010000-eng.htm#a5), Canadian Universities and Colleges participating in the Data Liberation Initiative (DLI) and is also available for order on the [Statistics Canada website](https://www150.statcan.gc.ca/n1/en/catalogue/452500112021001).
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is available for download through the SDA @ CHASS website at the University of Toronto to members of the University of Toronto community and is also available in EFT format when ordered from Statistics Canada.
3. *When will the dataset be distributed?*
	- It is already available.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- It is distributed to Canadian Universities and Colleges participating in the Data Liberation Initiative (DLI) under the [Data Liberation Initiative - Licence Agreement](https://www.statcan.gc.ca/en/dli/licence).
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- When accessing data through SDA @ CHASS, links to data are IP-address restricted. Off campus University of Toronto users must first log in to myaccess.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No.
7. *Any other comments?*
	- No.

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Statistics Canada hosts the dataset in their Public Use Microdata File (PUMF) Collection.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Contact PUMF at Statistics Canada at statcan.fmgd-pumf.statcan@canada.ca.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- No.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- No.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- N/A.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- No.
8. *Any other comments?*
	- No.
